analysis-pilot

### 2023-07-31 code/analysis-pilot.Rmd
add clean data, wrangle time partway

pilot_start=lubridate::ymd('2023-7-07') 
pilot_end=lubridate::ymd('2023-7-11')
```

```{r}
raw_data <- read.csv(here("data/rounds7.19.csv"), header = TRUE) %>% 
  filter(createdAt >= pilot_start) %>%
  filter(createdAt <= pilot_end) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  select(-chat) |> 
  pivot_longer(cols=starts_with('player'), names_to=c("playerId", "info"), names_prefix="player_", names_sep="_",
               values_to="values", values_transform=as.character, values_drop_na=T) %>% 
  filter(values!="") %>% 
  filter(playerId!=speaker) %>% 
  pivot_wider(names_from=info, values_from=values)

@@

@@

>>>>

pilot_start=lubridate::ymd('2023-07-07') 
pilot_end=lubridate::ymd('2023-07-12')

data_source <- "data/rounds.csv"
player_source <- "data/players.csv"

player_ids <- str_c("id", 3:12) # Ids 1, 2 were adult pilot test 
```

# Veronica works on wrangling transcripts here

```{r}

players <- read_csv(here(player_source)) |> filter(id %in% player_ids) |> select(id, playerId=`_id`)

games <- read_csv(here("data/games.csv"), col_types="ccc") |> mutate(offset_sec=lubridate::ms(offset) |> lubridate::period_to_seconds()) |> select(-offset)

```{r}

raw_data <- read.csv(here(data_source), header = TRUE) %>% 
  filter(createdAt >= pilot_start) %>%
  filter(createdAt <= pilot_end) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  select(-chat) |> 
  pivot_longer(cols=starts_with('player'), names_to=c("playerId", "info"), names_prefix="player_", names_sep="_",
               values_to="values", values_transform=as.character, values_drop_na=T) %>% 
  filter(values!="") %>% 
  filter(playerId!=speaker) %>% 
  pivot_wider(names_from=info, values_from=values) |> 
  left_join(players, by=c("playerId")) |> 
  select(-playerId) |> 
  rename(playerId=id) |> 
  left_join(players, by=c("speaker"="playerId")) |> 
  select(-speaker) |> 
  rename(speaker=id) |> 
  left_join(games) |> 
  rename(game=gameConfig) |> 
  select(-gameId, -offset_sec) |> 
  filter(!is.na(game)) |> 
  mutate(time=as.numeric(time))

@@

```{r}
#just for pilot, need to fix offset
fix <- raw_data |> filter(trialNum==0) |> select(game, time)

real_offset <- games |> left_join(fix, by=c("gameConfig"="game")) |> mutate(offset_sec=offset_sec-time/1000)

timing <- raw_data |> group_by(game) |> mutate(cum_time=cumsum(time), cum_sec=cum_time/1000+3*trialNum)

```{r}

wrangle_transcript <- function(game_num){
readxl::read_xlsx(here("data/clean_transcripts", str_c(game_num,".xlsx"))) |> 
  select(start, end, text, speaker) |> 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker))
}

#wrangle_transcript("game32")

real_offset$transcripts <- map_df(real_offset$gameConfig, wrangle_transcript)

transcripts <- real_offset |> unnest(transcripts) |> unnest(data)

# this section is janky as hell, but it does work

timed_transcripts <- transcripts |> mutate(start=start-offset_sec, end=end-offset_sec)
```

@@

#View(filtered_data)
```
